Data Appendix to \"The impact of weather events on schooling outcomes\

### 2020-04-24 data_appendix_all_years.Rmd
if this were a panel but it's not

model_simple <- plm(assist ~ floods + droughts, data = reg_data, model = "within")
summary(model_simple)
model_all <- plm(assist ~ floods + droughts + sex + age + lny + hhhead_educ + female_hhhead + urb_rur, data = reg_data, model = "within")
summary(model_all)
model_register <- plm(register ~ floods + droughts + sex + age + lny + hhhead_educ + female_hhhead + urb_rur, data = reg_data, model = "within")
summary(model_register)
```

>>>>

#set as panel data
panel <- plm.data(reg_data, index = c("id", "year"))
model_simple <- plm(assist ~ floods + droughts, data = reg_data, model = "within")
summary(model_simple)
model_all <- plm(assist ~ floods + droughts + sex + age + lny + hhhead_educ + female_hhhead + urb_rur, data = reg_data, model = "within")
summary(model_all)
model_register <- plm(register ~ floods + droughts + sex + age + lny + hhhead_educ + female_hhhead + urb_rur, data = reg_data, model = "within")
summary(model_register)
```
